Compiling refinement types to dependent types

### 2020-07-25 tex/paper.tex
Minor wording fix

All in all, our goal is to define $\Tranctx$, $\Tranty$ and $\Tranterm$
with ``metatypes''
\begin{align*}
  \Tranctx  & : \nonterm G \ctxok                             \longmapsto \nonterm{GC},                                     \\
  \Tranty   & : \nonterm G \vdash \nonterm{ts}                \longmapsto \nonterm{GC} \vdash \nonterm{tc} : \star,         \\
  \Tranterm & : \nonterm G \vdash \nonterm{es} : \nonterm{ts} \longmapsto \nonterm{GC} \vdash \nonterm{ec} : \nonterm{tc},
\end{align*}
Our helper functions $\tranty$ and $\tranterm$ are then defined to return the $\nonterm{tc}$ and $\nonterm{ec}$
from the right-hand sides above respectively.

>>>>

All in all, our goal is to define $\Tranctx$, $\Tranty$ and $\Tranterm$
with ``metatypes''
\begin{align*}
  \Tranctx  & : \nonterm G \ctxok                             \longmapsto \nonterm{GC},                                     \\
  \Tranty   & : \nonterm G \vdash \nonterm{ts}                \longmapsto \nonterm{GC} \vdash \nonterm{tc} : \star,         \\
  \Tranterm & : \nonterm G \vdash \nonterm{es} : \nonterm{ts} \longmapsto \nonterm{GC} \vdash \nonterm{ec} : \nonterm{tc},
\end{align*}
Our helper functions $\tranty$ and $\tranterm$ are then defined to return the $\nonterm{tc}$ and $\nonterm{ec}$
from the respective right-hand sides.
